HO unification from object language to meta language

### 2024-03-22 paper/main.tex
notatations

We use math mode for \Ho.

\begin{tabular}{ll}
  $\lambda x.\lambda y.F_{x y}$ & \elpiIn{lam x\ lam y\ uva F [x, y]} \\
  $f~ a$ &  \elpiIn{app[con "f", con "a"]}\\
  $\lambda x.F_{x} ~ a$ & \elpiIn{lam x\ app[uva F [x], con "a"]} \\
  $\lambda x.F_{x} ~ x$ & \elpiIn{lam x\ app[uva F [x], x]} \\
\end{tabular}

>>>>

When we write \Ho terms outside code blocks we prefer to use the
usual and more compact mathematical notation. However we need to
distinguish between the ``application'' of a unification variable
to its scope and the application of a term (possibly a unification
variable) to a list of arguments. We write the scope in subscript
and we use juxtaposition for application. Here a few examples:
\vspace{5pt}

\begin{tabular}{ll}
  $\lambda x.\lambda y.F_{x y}$ & \elpiIn{lam x\ lam y\ uva F [x, y]} \\
  $f~ a$ &  \elpiIn{app[con "f", con "a"]}\\
  $\lambda x.F_{x} ~ a$ & \elpiIn{lam x\ app[uva F [x], con "a"]} \\
  $\lambda x.F_{x} ~ x$ & \elpiIn{lam x\ app[uva F [x], x]} \\
\end{tabular}
\vspace{5pt}

\noindent
When detailing example we prefer to write links in mathematical notation,
as equations between terms in a context. The equality sign is subscripted with
kind of \elpiIn{baselink}. For example $\linkbetaM{x}{A}{F_x~a}$ corresponds to:
\begin{elpicode}
abs x\ val (link-beta (uva A []) (app[uva F [x],con "a"]))
\end{elpicode}
